Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-19 paper/responseToReviewers.tex

We would like to thank the editor and the reviewers for their comments and suggestions. Following these comments, we made several changes to the article, which are summarized here. The next sections list our answers to each of the reviewer's comments, with references to the revised manuscript where appropriate.

\section{Responses to the Associate Editor}

\begin{enumerate}

\item \emph{Line 40, $\alpha$ may appear in previous equations}

@@

The order of the figures and their corresponding text have been reversed.

\item \emph{The class accuracy Table III for Home and Residential area are singular. Authors shall discuss that.}

The text has been modified to discuss these results.

\item \emph{Complete caption of Fig. 5.}

The caption have been completed to help the readability of the figure.

@@

\item \emph{It is never specified what are the signals frequency sampling which we have to deduce to be 44100 Hz from line 9 page 3 "20kHz close to the Nyquist frequency of the audio recordings".}

\item \emph{"Wavelet scalogram" is used along all the paper but scalogram is only defined for wavelets since 
it is a scale-o-gram.}

This is true, but for readers less familiar with the terminology, we have opted to use this more redundant expression to express the fact that these derive from wavelet decompositions.

\item \emph{Line 60: auditory and modulation filter – nonsense.}

@@

\item \emph{Setting of $Q1$ shall be motivated.}

This has been added to the text.

\item \emph{Reproducibility:  data sets are publicly available, the author do not mention if they plan to make their model available.}

Experiments have been performed in the Matlab environment using open source libraries an all the authors are committed to comply to the reproducible research statements. The replication code is now available in beta, and will be soon stable.

\item \emph{In the last experience (Table III) GMM (MFCC) may be compared to SVM (MFCC) (in addition to SVM (logscat)). There is somewhere a high dimension effect that shall be clarified.}

@@

%They are added as supplementary material in manuscript central and will be available on the code repository.

\item \emph{The cross-validation analyses confirmed that the value T = 372 ms for the support of the low-pass filter is optimal when applying late integration by majority voting, but shall it adapted per classes  ?}

Although it is true that different values of $T$ could be appropriate for different classes (that is, the different sound objects present could be of different scale), we do not expect results to change significantly. This is because the sounds are of a similar nature (ambient, non-directed) and so any distinct object shouldn't be much longer or shorter in duration in one class compared to another. In addition, $T = 372\,\mathrm{ms}$ is at the longer end of the useful range of window sizes for which the scattering transform is useful, so it is unlikely that larger sizes would improve.

\item \emph{A table with the 2016 DCASE private results may be added (or replace Tab III).}

### 2016-12-19 paper/structureScene.tex
doubles as -> is also

\subsection{Wavelet scalogram}
Our convention for the Fourier transform of a continuous-time signal $\boldsymbol{x}(t)$ is $\boldsymbol{\hat{x}}(\omega) = \int_{-\infty}^{+\infty} x(t) \exp(- \mathrm{i} 2\pi \omega t) \; \mathrm{d}t$.
Let $\boldsymbol{\psi}(t)$ a complex-valued band-pass filter of
center frequency $\xi_1$ and bandwidth $\xi_1/Q_1$, where $Q_1$ is the quality factor of the filter.
A filter bank of wavelets is built by dilating $\boldsymbol{\psi}(t)$
according to a geometric sequence of scales $2^{\gamma_1/Q_1}$, obtaining
\begin{equation}
\boldsymbol{\psi_{\gamma_1}}(t) = 2^{-\gamma_1/Q_1} \boldsymbol{\psi}(2^{-\gamma_1/Q_1} t)\mbox{.}
\end{equation}
The variable $\gamma_1$ is a scale (an inverse log-frequency) taking integer values between $0$ and $(J_1 \times Q_1 - 1)$, where $J_1$ is the number of octaves spanned by the filter bank.
For each $\gamma_1$, the wavelet $\boldsymbol{\psi_{\gamma_1}}(t)$
has a center frequency of $2^{-\gamma_1/Q_1}\xi_1$ and a bandwidth of $2^{-\gamma_1/Q_1}\xi_1/Q_1$ resulting in the same quality factor $Q_1$ as $\boldsymbol{\psi}$.
In the sequel, we set $\xi_1$ to $20~\mathrm{kHz}$, $J_1$ to $10$, and the quality factor $Q_1$, which doubles as the number of wavelets per octave, to $8$. This results in the wavelet filters covering the whole range of human hearing, from $20~\mathrm{Hz}$ to $20~\mathrm{kHz}$. Setting $Q_1 = 8$ results in filters whose bandwidth approximates an equivalent rectangular bandwidth (ERB) scale.

>>>>

\subsection{Wavelet scalogram}
Our convention for the Fourier transform of a continuous-time signal $\boldsymbol{x}(t)$ is $\boldsymbol{\hat{x}}(\omega) = \int_{-\infty}^{+\infty} x(t) \exp(- \mathrm{i} 2\pi \omega t) \; \mathrm{d}t$.
Let $\boldsymbol{\psi}(t)$ a complex-valued band-pass filter of
center frequency $\xi_1$ and bandwidth $\xi_1/Q_1$, where $Q_1$ is the quality factor of the filter.
A filter bank of wavelets is built by dilating $\boldsymbol{\psi}(t)$
according to a geometric sequence of scales $2^{\gamma_1/Q_1}$, obtaining
\begin{equation}
\boldsymbol{\psi_{\gamma_1}}(t) = 2^{-\gamma_1/Q_1} \boldsymbol{\psi}(2^{-\gamma_1/Q_1} t)\mbox{.}
\end{equation}
The variable $\gamma_1$ is a scale (an inverse log-frequency) taking integer values between $0$ and $(J_1 \times Q_1 - 1)$, where $J_1$ is the number of octaves spanned by the filter bank.
For each $\gamma_1$, the wavelet $\boldsymbol{\psi_{\gamma_1}}(t)$
has a center frequency of $2^{-\gamma_1/Q_1}\xi_1$ and a bandwidth of $2^{-\gamma_1/Q_1}\xi_1/Q_1$ resulting in the same quality factor $Q_1$ as $\boldsymbol{\psi}$.
In the sequel, we set $\xi_1$ to $20~\mathrm{kHz}$, $J_1$ to $10$, and the quality factor $Q_1$, which is also the number of wavelets per octave, to $8$. This results in the wavelet filters covering the whole range of human hearing, from $20~\mathrm{Hz}$ to $20~\mathrm{kHz}$. Setting $Q_1 = 8$ results in filters whose bandwidth approximates an equivalent rectangular bandwidth (ERB) scale.
